---
title: "Resume Raúl Blé"
author: "Raúl Blé"
date: "`r Sys.Date()`"
output: 
  pagedown::html_resume:
self_contained: True
css: ['form.css']
editor_options: 
  chunk_output_type: console
---

```{r Chunk options, echo=FALSE}

knitr::opts_chunk$set(warning = F, message = F, echo = FALSE, results = 'asis')

```

Aside
================================================================================

```{r}
#You can input your logo in this chunk

```

Contact info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> raulgustavo1@gmail.com
- <i class="fa fa-phone"></i> 55 3052 - 8101
- <i class="fa fa-github"></i> github.com/RGBR98


Skills {#skills}
--------------------------------------------------------------------------------

- Great for managing unforeseen events, crisis, and stress situations.
- Great in sales and promotion of products and services

**IT:** 

- <i class="fa fa-laptop-code"></i> Office suite
- <i class="fa fa-laptop-code"></i> R (Shiny, MarkDown) 

**Languages**

- <i class="fa fa-globe-americas"></i> Spanish
- <i class="fa fa-globe-americas"></i> English (C1)


Main
================================================================================

Raúl Blé Rosique {#title}
--------------------------------------------------------------------------------

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
### (ITAM) Instituto Tecnológico Autónomo de México

Currently studying 6th semester in the Bachelor of Finance

Mexico City, Mexico

2017 - To date



Experience {data-icon=briefcase} 
--------------------------------------------------------------------------------

### Hyundai pedregal 

Product previewer 

Mexico City, Mexico

2016 - 2017


### Hyundai Pedregal 

Sales associate and Web manager 

Mexico City, Mexico

2019 - 2020

**Expertise & certifications**

- Purchase contract analysis and distribution for automobile acquisition. 
- Web management and control for sales associates.
- Certification, "Inducción a las ventas".
- Certification, "Tripié de ventas".
- Course, “Supervición de ventas por internet”. 
- Course, “Lealtad de portafolio”.

### Compucom GSC México

L1 technician for GameStop

Mexico City, Mexico

2020 - To date

**Expertise**

 - Manager of the "Surface project", GameStop (Groups between 10 & 20 people).
 - Creation of an automatized analysis for the surface project with R (programming language).
 - Participation on the Windows 10 upgrade project, GameStop.
 - Excellent Quality Assurance and User satisfaction.
 
 Extra Curricular Activities {data-icon=file-alt}
--------------------------------------------------------------------------------
### UANMUN

Second place in "Derechos humanos" committee

Anahuac, Mexico

2015

### Ruedafest 2019

Second place, group coreography

Guadalajara, Mexico

2019

- Group co-leader for the Salsa group (Around 20 people under management)


